### 2022-05-24 GB_3species.Rmd
New file to aling with server
rec cv =0.55

#profvis::profvis({
#original settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 10472, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                   K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

#increasing population
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 40000, "b" = 4301*10, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 45000 , "b" = 10472*6, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 100000, "b" = 40530*10, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.1, "spp3" = .334+.45), #NEED F
                   K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

#constant population
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 10472, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358+2, "spp2" = .2728+.511+.05, "spp3" = .334-.025), #NEED F
                   K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

@@

start_time <- Sys.time() # record start time

  res<- run_sim(sim_init = sim,
                pop_init = Pop,
                move_cov = moveCov,
                fleets_init = fleets,
                hab_init = hab,
                save_pop_bio = TRUE,
                survey = NULL, #surv_random, will try to survey after simulation
                closure = NULL,
                InParallel = TRUE,
                nz = nonzero_idx)  #does it runin parallel? Doesnt seem like it

end_time <- Sys.time() # record end time
tot_time <- end_time - start_time # calculate duration of lrren() example

>>>>

#profvis::profvis({
#original settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0.55),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 10472, "cv" = 0.55),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0.55)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                     K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

#increasing population
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 40000, "b" = 4301*10, "cv" = 0.55),
                                       "spp2" = c("model" = "BH", "a" = 45000 , "b" = 10472*6, "cv" = 0.55),
                                       "spp3" = c("model" = "BH", "a" = 100000, "b" = 40530*10, "cv" = 0.55)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.1, "spp3" = .334+.45), #NEED F
                     K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

#constant population
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0.55),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 10472, "cv" = 0.55),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0.55)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358+2, "spp2" = .2728+.511+.05, "spp3" = .334-.025), #NEED F
                     K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

#decreasing populations
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 50000, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 1.071946e+12, "b" = 2.296998e+12, "cv" = 0.55),
                                       "spp2" = c("model" = "BH", "a" = 389480664 , "b" = 980163673, "cv" = 0.55),
                                       "spp3" = c("model" = "BH", "a" = 497371062, "b" = 2078612769, "cv" = 0.55)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                     K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

@@

    start_time <- Sys.time() # record start time
    p<-profmem::profmem({

    res<- run_sim(sim_init = sim,
                  pop_init = Pop,
                  move_cov = moveCov,
                  fleets_init = fleets,
                  hab_init = hab,
                  save_pop_bio = TRUE,
                  survey = NULL, #surv_random, will try to survey after simulation
                  closure = NULL,
                  InParallel = TRUE,
                  nz = nonzero_idx)  #does it runin parallel? Doesnt seem like it
    })
    end_time <- Sys.time() # record end time
    tot_time <- end_time - start_time # calculate duration of lrren() example
